### 2015-07-06 narrative/evaluation.tex
filling the lines so the text is somewhat readable

\section{Evaluation}
\label{sec:evaluation}
In order to determine if our guiding principles are being met, and we can optimize the system from these guiding principles, 
we will evaluate our work using the Table~\ref{table:eval}.

>>>>

\section{Evaluation}
\label{sec:evaluation}

In order to determine if our guiding principles are being met, and we can optimize the system from these guiding principles, 
we will evaluate our work using the Table~\ref{table:eval}.
